---
output:
  html_document: default
  pdf_document: default
---
Analyzing relationship between miles per gallon and automatic or manual transmission car
=====================================================================
## Cuiming Zheng
##Sep 8,2017
# Executive summary
 
 
 
 

# getting data
following is R code  to download training and testing data and read data in r
```{r echo = TRUE,message=FALSE, warning=FALSE }
setwd("C:/Users/u292859/Desktop/Reproducible Research")
url="https://d396qusza40orc.cloudfront.net/predmachlearn/pm
l-training.csv"

download.file(url,destfile="C:/Users/u292859/Desktop/Reproducible Research/pml-training.csv")
data<-read.csv("pml-training.csv" )
str(data)
dim(data)
URL="https://d396qusza40orc.cloudfront.net/predmachlearn/pm
l-testing.csv"
download.file(url,destfile="C:/Users/u292859/Desktop/Reproducible Research/pml-test.csv")
testdata<-read.csv("pml-test.csv" )
dim(new)
```


# clean data

following are R code to remove NA variables
```{r echo = TRUE}
nacol<-which(colSums(is.na(data))>19000)
newtrain<-data[,-c(nacol)]
```
#preprocess data to remove near zero variables
following are r code preprocess data, we also remove the first 6 variables that is not related to the project.
```{r echo = TRUE}
library(caret)
nsv<-nearZeroVar(newtrain)
new<-newtrain[,-nsv]
protrain<-newtrain[,-c(1:6)]
```

# create data partation on cleanned and preprocessed training dataset

Following are R code to create data partition
```{r echo = TRUE}
inTrain = createDataPartition(protrain$classe, p = 3/4)[[1]]
training = protrain[ inTrain,]
testing = protrain[-inTrain,]
dim(training)
dim(testing)
```

# multiple models analsyis and  model selection
following are R code for fit linear regression with single variable transmission
```{r echo = TRUE}

```

``{r echo = TRUE}

`
#  conclusions
